Augmenting the DonorsChoose.org Corpus for Meta-Learning

### 2018-12-10 doc/compact paper/main.tex
Introduce a compact paper with the same content

\documentclass[runningheads]{llncs}
	\usepackage[ngerman,english]{babel}  % Language specification
	\usepackage{varioref}  % Better references but possibly unstable
	\usepackage[T1]{fontenc}  % Output umlauts in a PDF
	\usepackage[utf8]{inputenc}
	\usepackage{pslatex}
	\usepackage{amsmath}
	\usepackage{multirow}
	\usepackage{ellipsis}
	\usepackage{textcomp}
	\usepackage{longtable}
	\usepackage{rotating}
	\usepackage[section]{placeins}

@@

	% Display URLs in blue roman font if using hyperref to comply with Springer's eBook style
	\renewcommand\UrlFont{\color{blue}\rmfamily}

@@

	\lstset{basicstyle=\ttfamily,breaklines=true}  % Prettier code highlighting style
	\pagestyle{myheadings}  % Prettier page format with header but without footer

@@

\titlerunning{Augmenting the DonorsChoose.org Corpus for Meta-Learning}  % Abbreviated title
\title{Augmenting the DonorsChoose.org Corpus for Meta-Learning%
	\thanks{This publication emanated from research conducted with the financial support of Science Foundation Ireland (SFI) under Grant Number 13/RC/2106.}
}
\author{Gordian~Edenhofer\inst{1,2} \and Joeran~Beel\inst{1,2} \and Andrew~Collins\inst{1} \and Akiko~Aizawa\inst{2}}
\authorrunning{G. Edenhofer et al.}  % Abbreviated author field
\institute{
	Trinity College Dublin, School of Computer Science \& Statistics, ADAPT Centre, Ireland\\ \and
	National Institute of Informatics Tokyo, Digital Content and Media Sciences Division, Japan\\ \email{beelj@tcd.ie, collinsa@tcd.ie, aizawa@nii.ac.jp}
}

\maketitle  % Typeset the header of the contribution
\markboth{}{}  % Clear the section and author from the page header

\begin{abstract}
The DonorsChoose.org dataset of past donations provides a big and feature-rich corpus of users and items. The dataset matches donors to projects in which they might be interested in and hence is intrinsically about recommendations. Due to the availability of detailed item-, user- and transaction-features, this corpus represents a suitable candidate for meta-learning approaches to be tested. This study aims at providing an augmented corpus for further recommender systems studies to test and evaluate meta-learning approaches. In the augmentation, metadata of collaborative and content-based filtering techniques is amended to the corpus. It is further extended with aggregated statistics for users and transactions and an exemplary meta-learning experiment. The performance in the learning subsystem is measured via the recall of recommended items in a Top-N test set. The augmented dataset and the source code are released into the public domain at GitHub:BeelGroup/Augmented-DonorsChoose.org-Dataset.

\keywords{recommender systems \and meta-learning \and dataset augmentation \and ensemble learning \and hybrid recommenders.}
\end{abstract}

@@

\begin{table}[ht]
	\centering
	\caption{Illustrative example of the overall design of the augmented transaction table with amended learning subsystem performance scores, statistics and meta-learner information.}
	\label{tab:IllustrativeTable}
	\includegraphics[width=\textwidth,height=0.5\textheight,keepaspectratio]{{{../res/Illustrative example of the overall design of the augmented transaction table}}}
\end{table}

@@

\begin{figure}[ht]
	\centering
	\includegraphics[width=\textwidth,height=0.3\textheight,keepaspectratio]{{{../res/Learning subsystem - Position in Top-N test set}}}
	\caption{Statistical features of the distributions of the recall-positions of the learning subsystem. The dashed green lines indicate the mean, the straight orange lines the median. The percentage below each algorithm indicates how often it is the best possible algorithm. To resolve a draw deterministically, the ``best'' algorithm is decided in alphabetic order.}
	\label{fig:MetaLearnerStatistics}
\end{figure}

@@

\begin{figure}[ht]
	\centering
	\includegraphics[width=\textwidth,height=0.3\textheight,keepaspectratio]{{{../res/Meta-learner Performance - Average position in Top-N test set for various meta-learner algorithms with augmented learning subsystem filtering techniques}}}
	\caption{Performance of the meta-learner system addressing the ASP. The dashed orange line represents the overall best algorithm, i.e., TF-IDF.}
	\label{fig:MetaLearnerPerformance}
\end{figure}

@@

\begin{appendix}
	\printbibliography[heading=bibintoc]
\end{appendix}

>>>>

\documentclass{IEEEtran}
	\usepackage{csquotes}  % For usage with the IEEEtran document class as to avoid warning
	\usepackage[ngerman,english]{babel}  % Language specification
	\usepackage{varioref}  % Better references but possibly unstable
	\usepackage[T1]{fontenc}  % Output umlauts in a PDF
	\usepackage[utf8]{inputenc}
	\usepackage{pslatex}
	\usepackage{amsmath}
	\usepackage{multirow}
	\usepackage{ellipsis}
	\usepackage{textcomp}
	\usepackage{longtable}
	\usepackage{rotating}
	\usepackage[section]{placeins}

@@

	% Display URLs in blue roman font if using hyperref to comply with Springer's eBook style
	%\renewcommand\UrlFont{\color{blue}\rmfamily}

@@

	\lstset{basicstyle=\ttfamily,breaklines=true}  % Prettier code highlighting style
	%\pagestyle{myheadings}  % Prettier page format with header but without footer

@@

%\titlerunning{Augmenting the DonorsChoose.org Corpus for Meta-Learning}  % Abbreviated title
\title{Augmenting the DonorsChoose.org Corpus for Meta-Learning}
\author{
	\IEEEauthorblockN{
		Gordian~Edenhofer\IEEEauthorrefmark{1}\IEEEauthorrefmark{2},
		Joeran~Beel\IEEEauthorrefmark{1}\IEEEauthorrefmark{2}%
		\thanks{This publication emanated from research conducted with the financial support of Science Foundation Ireland (SFI) under Grant Number 13/RC/2106.},
		Andrew~Collins\IEEEauthorrefmark{1} and
		Akiko~Aizawa\IEEEauthorrefmark{2}
	}

	\IEEEauthorblockA{
		\IEEEauthorrefmark{1}Trinity College Dublin, School of Computer Science \& Statistics, ADAPT Centre, Ireland
	}

	\IEEEauthorblockA{
		\IEEEauthorrefmark{2}National Institute of Informatics Tokyo, Digital Content and Media Sciences Division, Japan
	}

	\href{mailto:beelj@tcd.ie}{beelj@tcd.ie},
	\href{mailto:collinsa@tcd.ie}{collinsa@tcd.ie},
	\href{mailto:aizawa@nii.ac.jp}{aizawa@nii.ac.jp}
}
%\authorrunning{G. Edenhofer et al.}  % Abbreviated author field

\maketitle  % Typeset the header of the contribution
%\markboth{}{}  % Clear the section and author from page headers

\begin{abstract}
The DonorsChoose.org dataset of past donations provides a big and feature-rich corpus of users and items. The dataset matches donors to projects in which they might be interested in and hence is intrinsically about recommendations. Due to the availability of detailed item-, user- and transaction-features, this corpus represents a suitable candidate for meta-learning approaches to be tested. This study aims at providing an augmented corpus for further recommender systems studies to test and evaluate meta-learning approaches. In the augmentation, metadata of collaborative and content-based filtering techniques is amended to the corpus. It is further extended with aggregated statistics for users and transactions and an exemplary meta-learning experiment. The performance in the learning subsystem is measured via the recall of recommended items in a Top-N test set. The augmented dataset and the source code are released into the public domain at GitHub:BeelGroup/Augmented-DonorsChoose.org-Dataset.
\end{abstract}

\begin{IEEEkeywords}
	recommender systems, meta-learning, dataset augmentation, ensemble learning, hybrid recommenders.
\end{IEEEkeywords}

@@

\begin{table*}[ht]
	\centering
	\caption{Illustrative example of the overall design of the augmented transaction table with amended learning subsystem performance scores, statistics and meta-learner information.}
	\label{tab:IllustrativeTable}
	\includegraphics[width=\textwidth,height=0.5\textheight,keepaspectratio]{{{../res/Illustrative example of the overall design of the augmented transaction table}}}
\end{table*}

@@

\begin{figure}[ht]
	\centering
	\includegraphics[width=0.45\textwidth,height=\textheight,keepaspectratio]{{{../res/Learning subsystem - Position in Top-N test set}}}
	\caption{Statistical features of the distributions of the recall-positions of the learning subsystem. The dashed green lines indicate the mean, the straight orange lines the median. The percentage below each algorithm indicates how often it is the best possible algorithm. To resolve a draw deterministically, the ``best'' algorithm is decided in alphabetic order.}
	\label{fig:MetaLearnerStatistics}
\end{figure}

@@

\begin{figure}[ht]
	\centering
	\includegraphics[width=0.45\textwidth,height=\textheight,keepaspectratio]{{{../res/Meta-learner Performance - Average position in Top-N test set for various meta-learner algorithms with augmented learning subsystem filtering techniques}}}
	\caption{Performance of the meta-learner system addressing the ASP. The dashed orange line represents the overall best algorithm, i.e., TF-IDF.}
	\label{fig:MetaLearnerPerformance}
\end{figure}

@@

\printbibliography[heading=bibintoc]
